\section{Getting Around -- Site Navigation and Performing Tasks}

After logging in (and performing most actions), you will be presented with a calendar view of the current month's events.

There are three different ways to see the currently booked events: by month, by week, and by day. You can switch between each view by clicking the buttons in the upper-right hand corner of the screen.


\subsection{Events}

Events are in essence room bookings.

In all views, events are colour coded according to their status: tentative (blue), confirmed (green), or rejected (red). Only Administrator-level users can make confirmed bookings or change booking statuses. All other user levels may only create tentative (requested) events.

Administrator-level users can be drag-and-drop events to different days (month or week views), times (week or day views), or rooms (day view only). If you are not an administrator, and you wish to change an event, please contact the Storefront.


% Show view buttons circled in main view


\subsection{Navigation by Month}

This is the default view that you will see after logging in.

By default, the month presented is the current month. To view a different month, navigate backwards and forwards using the arrow buttons.


\subsection{Navigation by Week}

The columns are days of the week, and the rows are booking times.

By default, the week presented is the current week. To view a different week, navigate backwards and forwards using the arrow buttons.


\subsection{Navigation by Day}

The columns are bookable rooms, and the rows are booking times.

By default, the day presented is the current day. To view a different day, navigate backwards and forwards using the arrow buttons.


\subsection{Performing Tasks -- The Toolbar}

The Toolbar is the grey bar that appears at the top of every page. The Storefront logo on the left side of the Toolbar is a drop-down menu that shows a list of tasks that you can perform. To perform a task, hover over the Storefront logo, and click one of the options that appears.

For example, if you want to add a new event, select the ``Add New Event'' option from the drop-down menu in the Toolbar.

The Toolbar also has a ``Logout'' button in the upper-right corner.


