\section{Administrator Tasks}

This section describes tasks that can be performed by Administrator-level users, using the drop-down menu in the Toolbar.

If you are not an Administrator, please refer to either the ``Front-Desk Staff Tasks'' chapter, or the ``Storefront Partner Tasks'' chapter.


\subsection{Adding a New User}

To add a new user to the system, select ``Add New User'' from the drop-down menu in the Toolbar. You will be directed to the ``Add New User'' form.

Fill out all the required fields in the form, and click ``Continue''. If you want to clear the form, click 'Reset'.


\subsection{Editing an Existing User}

To edit an existing user, select ``Edit User'' from the drop-down menu in the Toolbar. You will be directed to the ``Edit User'' form.

Fill out all the required fields in the form, and click ``Save''. If you want to delete the user, click ``Delete''. You cannot delete your own account, even as an Administrator.


\subsection{Adding a New Storefront Partner}

To add a new Storefront Partner to the system, select ``Add New Client'' from the drop-down menu in the Toolbar. You will be directed to the ``Add New Client'' form.

Fill out all the required fields in the form, and click ``Continue''. If you want to clear the form, click 'Reset'.


\subsection{Editing an Existing Storefront Partner}

To edit an existing Storefront Partner, select ``Edit Client'' from the drop-down menu in the Toolbar. You will be directed to the ``Edit Client'' form.

Fill out all the required fields in the form, and click ``Save''. If you want to delete the Partner, click ``Delete''.


\subsection{Adding a New Event}

To add a new event to the system, select ``New Event'' from the drop-down menu in the Toolbar. You will be directed to the ``Add New Booking'' form.

Fill out all the required fields in the form, and click ``Continue''. If you want to clear the form, click 'Reset'.


\subsection{Editing an Existing Event}

To edit an existing event, select ``Edit Event'' from the drop-down menu in the Toolbar. You will be directed to the ``Edit Bookings'' form.

Fill out all the required fields in the form, and click ``Save''. If you want to delete the event, click ``Delete''.


\subsection{Changing Your Password}

To change your password, select ``Update Password'' from the drop-down menu in the Toolbar. You will be directed to the ``Update Password'' form.

Fill out all the required fields in the form, and click ``Change Password''.


\subsection{Viewing a Map of Bookable Storefront Spaces}

To view a map of the Storefront facilities, select ``Rooms'' from the drop-down menu in the Toolbar. You will be directed to a map-view of the Storefront. Rooms outlined in green are bookable through the Calendar system. Hover over a room to see its details, including its capacity and any notes made about it.


\subsection{Event Shortcuts}

In the month, week, or day views, Administrators can drag-and-drop events to different days (month or week views), times (week or day views), or rooms (day view only).

Administrators can also confirm tentative bookings by single left-clicking on the event in any view. To edit the event, double left-click on it.

% Show view buttons circled in main view

