\section{Storefront Partner (`Client') Tasks}

This section describes tasks that can be performed by Partner-level (Client-level) users, using the drop-down menu in the Toolbar.

If you are not a Storefront Partner, please refer to either the ``Front-Desk Staff Tasks'' chapter, or the ``Administrator Tasks'' chapter.


\subsection{Adding a New Event}

To add a new event to the system, select ``New Event'' from the drop-down menu in the Toolbar. You will be directed to the ``Add New Booking'' form.

Fill out all the required fields in the form, and click ``Continue''. If you want to clear the form, click 'Reset'.

As a Partner, you may only add \textit{tentative} (\textit{requested}) events; an Administrator will need to confirm your room booking.


\subsection{Editing an Existing Event}

To edit an existing event, select ``Edit Event'' from the drop-down menu in the Toolbar. You will be directed to the ``Edit Bookings'' form.

Fill out all the required fields in the form, and click ``Save''. If you want to delete the event, click ``Delete''.

As a Partner, you may only edit your own events. If you edit a non-tentative booking, it will become tentative; an Administrator will need to confirm the new booking details.


\subsection{Changing Your Password}

To change your password, select ``Update Password'' from the drop-down menu in the Toolbar. You will be directed to the ``Update Password'' form.

Fill out all the required fields in the form, and click ``Change Password''.


\subsection{Viewing a Map of Bookable Storefront Spaces}

To view a map of the Storefront facilities, select ``Rooms'' from the drop-down menu in the Toolbar. You will be directed to a map-view of the Storefront. Rooms outlined in green are bookable through the Calendar system. Hover over a room to see its details, including its capacity and any notes made about it.


\subsection{Event Shortcuts}

Partners can edit their own events by double left-clicking on them. Double clicking on another Partner's event simply brings up the ``Edit Bookings'' form.

